The Evolution of Phenotypically Invariant Genetic Networks

### 2020-06-18 kalman_walk_paper.tex
added refs

Structural plasticity has been argued to be necessary for natural selection \citep{edelman2001degeneracy}, 
as it may function as a mechanism for biological robustness and evolvability, or manifest as 
\emph{canalization} \citep{whitacre2010degeneracy}. Degeneracy of the genetic code, and of genetic networks, 
for instance, can make sequences more fault-tolerant to mutations \citep{sonneborn1965degeneracy} and open up pathways to adaptation \citep{wagner2008robustness}.
Codon degeneracy can also enable the evolution of neutral and nearly neutral molecular changes \citep{kimura1968genetic},
and perhaps even contribute to the formation of new species \citep{gavrilets2014models}.

>>>>

Structural plasticity has been argued to be necessary for natural selection \citep{edelman2001degeneracy}, 
as it may function as a mechanism for biological robustness and evolvability, or manifest as 
\emph{canalization} \citep{whitacre2010degeneracy}. Degeneracy of the genetic code, and of genetic networks, 
for instance, can make sequences more fault-tolerant to mutations \citep{sonneborn1965degeneracy} and open up pathways to adaptation \citep{wagner2008robustness}.
Structural plasticity can also enable the evolution of neutral and nearly neutral molecular changes \citep{kimura1968genetic},
and perhaps even contribute to the formation of new species \citep{gavrilets2014models}.
